---
title: "R Notebook"
output: html_notebook
---

# Inferring Cultural States from Population Reading Activity
In order to infer cultural states from population reading activity,
we need to $a)$ understand a bit about cultural states, and $b)$ understand a bit about reading activity. That is what this notebook is about—conducting exploratory data analysis on the European Social Survey data and the Wikipedia data.

## European Social Survey (ESS)

The ESS refers to a biannual (every second year) survey conducted in various European countries,
focusing on cultural values and attitudes, and how these connect to media, politics and more.
I'm intending to use the ESS data to evaluate (and improve) the predictions I am making about
culture from the Wiki data. I'd have loved is the ESS data was annual, but unfortunately it is
not. There are only three ESS rounds for which I have Wiki data. I'm considering constructing
intermediate rounds by averaging out the value between rounds 7 and 8, and round 8 and 9, but
I digress. Let's load in the data (we got rounds 7, 8, 9 and a bunch of non country specific
questions):

```{r}
ess.path <- "../data/ess/ESS1-9e01_1.csv"
ess <- read.csv2(ess.path, sep = ',')
```

And now lets play around with it a little:
```{r}
names(ess)
```
