---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

# Inferring Cultural States from Population Reading Activity
In order to infer cultural states from population reading activity,
we need to $a)$ understand a bit about cultural states, and $b)$ understand a bit about reading activity. That is what this notebook is about—conducting exploratory data analysis on the European Social Survey data and the Wikipedia data.

## European Social Survey (ESS)

The ESS refers to a biannual (every second year) survey conducted in various European countries,
focusing on cultural values and attitudes, and how these connect to media, politics and more.
I'm intending to use the ESS data to evaluate (and improve) the predictions I am making about
culture from the Wiki data. I'd have loved is the ESS data was annual, but unfortunately it is
not. There are only three ESS rounds for which I have Wiki data. I'm considering constructing
intermediate rounds by averaging out the value between rounds 7 and 8, and round 8 and 9, but
I digress. Let's load in the data (we got rounds 7, 8, 9 and a bunch of non country specific
questions):

```{r}
ess.path <- "../data/ess/ESS1-9e01_1.csv"
ess <- read.csv(ess.path)
ess$essround <- as.factor(ess$essround)
```

We got `r length(names(ess))` different columns. That's a bit overwhelming. Which of these are useful?
How do they evolve through time? How are the distributions within the different countries?
There's a weight column. How do I use that? Let's see what countries we have to deal with:
```{r}
cat(unique(ess$cntry))
``` 

So there's a lot of country codes we know in there. Let's make a function that takes in a country and a feature, and plots it through time:

```{r}
# get all rows related to specific country
get.country <- function(country.code) {
  country.df <- subset(ess, cntry == country.code) 
  return(country.df)
}

# get all columns related to specific question
get.feature <- function(country.df, feature.name) {
  country.feature.df <- country.df %>%
    select(essround, feature.name)
  country.feature.df[,2] <- as.numeric(country.feature.df[,2])
  return(country.feature.df)
}

# remove weired values
do.filter <- function(country.feature.df) {
  country.feature.filter.df <- subset(country.feature.df, country.feature.df[,2] <= 10)
  return(country.feature.filter.df)
}

# plot a histogram
plot.feature <- function(country.code, feature.name) {
  country <- get.country(country.code)
  country.feature <- get.feature(country, feature.name)  
  country.feature.filter <- do.filter(country.feature)
  return(ggplot(country.feature.filter, aes(x = !!rlang::sym(feature.name), fill=as.factor(essround))) + geom_histogram(position='dodge', binwidth = .5) + ggtitle(country.code))
}
```

So we now have a way to get a country, and a feature, and plot a histogram for the different rounds. Next, let's look at a bunch of stuff:

```{r}
countries <- c('DE', 'DK', 'FI', 'NO', 'FR', 'IT', 'NL', 'SE', 'IS', 'DE', 'PL', 'ES')
for (country in countries) {
  plot(plot.feature(country, 'happy'))
}
```

### Distributuion of factors
On question: what's the distribution of the dofferent factors? Is it gausian? If it is, great! Than I can have my metric be how many standard devation I'm on average away from the true thing. Lets load in this shit


### Distribution of Human values stuffs
``` {r}
data <- read.csv('data/var.csv')
for (col in data) {
  plot(density(col))
}
```













